% This is part of the FinalReport document.
% Copyright (C) 2011 Piyabhum Sornpaisarn, Andrew Busse, Michael Hodgson, John Charlesworth, Paramithi Svastisinha
% See the file COPYING in FinalReport/ for copying conditions.

%% ----------------------------------------------------------------
\chapter{Design Decisions}
%% ----------------------------------------------------------------
Throughout the design and implementation of the project there were many points
at which decisions were made about the design of the system. This chapter attempts
to give an insight into some of the design decisions taken throughout the project with
a discussion of the alternative choices that were open to us at the time and the reasons
why a particular choice was made.

This chapter also details thel milestones of the project. These milestones can be seen in section \ref{sec:amended_milestones}.

\input{approaches_considered_camera}

\input{approaches_considered_local_storage}

\input{approaches_considered_payload}

\input{approaches_considered_jpeg_manipulation}

\input{approaches_considered_GUI}


\section{Physical Implementation (ab)}

Our specification states that the final module delivered to the customer 
should be on PCB, if time permits. Using existing breakout board type devices 
(such as the Arduino) and a daughter board would make the project far cheaper for 
one-off applications (one-off PCBs can be rather expensive) while still fitting 
this specification point, 
but would increase construction time to reproduce it, and increase the weight 
and volume of the module, two critical components of the project.

However, producing a bespoke PCB has the advantage of being smaller 
and lighter, and assembly could be handled by an external company.

Producing a stripboard solution would be implemented only if time and budgetary constraints are against us: 
whilst being the cheapest option, it would be larger than a PCB solution and not as robust.
	
\subsection{Power Source}

We also need to consider how such a module will be powered, and plan for both the following considerations:

\subsubsection{Approach: Battery Powered}

Providing a header on our final payload to attach an external power source 
should the Autopilot not be able to provide enough power would seem a 
sensible option. As this battery is likely to be Lithium-Ion or 
Lithium-Polymer, implementing a charging circuit may be considered, but would 
be dangerous to test. (Lithium Polymer batteries are prone to damage if incorrectly charged)

\subsubsection{Approach: Autopilot Powered}

It should be possible to source enough power from the Autopilot, which can 
comfortably provide up to 200mA at 3.3V. Designing our module to be as low-powered 
as possible would be beneficial (this extends the time the autopilot will be 
able to fly)

\input{milestones_amended}
