% This is part of the FinalReport document.
% Copyright (C) 2011 Piyabhum Sornpaisarn, Andrew Busse, Michael Hodgson, John Charlesworth, Paramithi Svastisinha
% See the file COPYING in FinalReport/ for copying conditions.

\bibliographystyle{ecs}

\begin{thebibliography}{9}

	\bibitem{SkyCircuits} SkyCircuits Ltd. Web. 13th Dec. 2011 \url{http://www.skycircuits.com/}

	\bibitem{SULSA} SULSA \emph{The "Southampton University Laser Sintered Aircraft} Web. 13th Dec. 2011 \url{http://www.soton.ac.uk/~decode/index_files/Page804.htm}

	\bibitem{SC_Press} New Scientist \emph{3D printing: The world's first printed plane} Web. 13th Dec. 2011 \url{http://www.newscientist.com/article/dn20737-3d-printing-the-worlds-first-printed-plane.html}

	\bibitem{SC2} SkyCircuits \emph{SC2 autopilot module} Web. 14th Dec. 2011 \url{http://www.skycircuits.com/autopilot/sc2}

	\bibitem{tortorella_jpeg_enc} Tortorella, Richard. \emph{Image Doctoring: JPEG Encoding and Analysis}. Rep. NARCAP, May 2009. Web. 11 Oct. 2011. \url{http://www.narcap.org/reports/narcap_IR-01_DigHoaxing.pdf}.
	
	\bibitem{exif_std} Japan Electronics and Information Technology Industries Association (JEITA). \emph{Digital Still Camera Image File Format Standard (Exchangeable Image File Format for Digital Still Cameras: Exif)} Version 2.2. Tech. Japan Electronic Industry Development Association (JEIDA), 12 June 1998. Web. 14 Oct. 2011 \url{http://www.exif.org/Exif2-2.PDF}.
	
	\bibitem{netravali_digital_repr} Netravali, Arun N., and Barry G. Haskell. \emph{Digital Pictures: Representation and Compression}. New York: Plenum, 1988. Print. 
	
	\bibitem{jpeg_layout} \emph{JPEG File Layout and Format}. Original URL: \\http://www.funducode.com/freec/Fileformats/format3/format3b.htm (defunct).\\DCube Software Technologies, 5 July 2002. Web. 28 Oct. 2011. \url{http://class.ee.iastate.edu/ee528/Reading%20material/JPEG_File_Format.pdf}
	
	\bibitem{winzip_jpeg_compression} WinZip® International LLC. \emph{JPEG Compression}. Tech. Version 1.0. 11 Sept. 2008. Web. 28 Oct. 2011. \url{http://www.winzip.com/wz_jpg_comp.pdf}.
	
	\bibitem{poynton_chroma_subsampling} Poynton, Charles. \emph{Chroma Subsampling Notation.} Charles Poynton. 24 Jan. 2008. Web. 31 Oct. 2011. \url{http://poynton.com/PDFs/Chroma_subsampling_notation.pdf}.
	
	\bibitem{kerr_chroma_subsampling} Kerr, Douglas A. \emph{Chrominance Subsampling in Digital Images}. Rep. Issue 2. 3 Dec. 2009. Web. 31 Oct. 2011. \url{http://dougkerr.net/pumpkin/articles/Subsampling.pdf}.
	
	\bibitem{hass_impulse_jpeg} Hass, Calvin. \emph{ImpulseAdventure - Digital Photography Articles.} 2008. Web. 22 Nov. 2011. \url{http://www.impulseadventure.com/photo/}.
	
	\bibitem{ucam_datasheet} 4D Systems. \emph{uCam Serial JPEG Camera Module Data Sheet} 8 Jul. 2010. \url{http://www.4dsystems.com.au/downloads/micro-CAM/Docs/uCAM-DS-rev4.pdf}.

	\bibitem{software_serial} Arduino. \emph{SoftwareSerial Library.} Web. 9th Dec. 2011 \url{http://www.arduino.cc/en/Reference/SoftwareSerial}.

	\bibitem{arduino_sd_library} Arduino. \emph{SD Library.} Web. 10th Dec. 2011 \url{http://www.arduino.cc/en/Reference/SD}.
	
	\bibitem{arduino_serial_library} Arduino. \emph{Serial Library.} Web. 1st Dec. 2011 \url{http://www.arduino.cc/en/Reference/Serial}.

	\bibitem{atmega644p} Atmel. \emph{ATMega644P} Web. 10th Dec. 2011 \url{http://www.atmel.com/dyn/products/product_card.asp?part_id=3896}

	\bibitem{sanguino} Sanguino. \emph{What is Sanguino?} Web. 10th Dec. 2011 \url{http://sanguino.cc/}.

	\bibitem{mbed} mbed. \emph{Welcome to mbed!} Web. 10th Dec. 2011 \url{http://mbed.org/}.

	\bibitem{olimexino} Olimex. \emph{Olimexino-stm32 development board Users Manual} Web. Oct. 2011 \url{http://www.olimex.com/dev/DUINO/OLIMEXINO-STM32/OLIMEXINO-STM32.pdf}.

	\bibitem{github} Github. \emph{Our "Official", Central Repository} Web. 11th Dec. 2011 \url{https://github.com/uavcamera/uavcamera}

	\bibitem{go-naked} \emph{Spirit Circuits Go Naked} Web. 11th Dec. 2011 \url{http://www.spiritcircuits.com/services/go-naked}
	
	\bibitem{peak_netFrame} C.D. CĂLEANU, V. TIPONUŢ, I. BOGDANOV, S. IONEL, I. LIE \emph{C\# and .NET Framework for uC communication protocol Proceedings of the 11th WSEAS International Conference on COMPUTERS, Agios Nikolaos, Crete Island, Greece, July 26-28, 2007
implementation} 2008. Web. 22 Nov. 2011.
\url{www.wseas.us/e-library/conferences/2007cscc/papers/561-338.pdf}.

	\bibitem{tsuiK} Kakit Tsui \emph{Ad Hoc Network:Generic USB Device Driver Development} (2003)
\url{http://crisp.ece.cornell.edu/mengproj/alan_report.doc}.

	\bibitem{keithC} Keith Clark,Peter J. Robinson,Richard Hagen.(2001) Multi-threading and message communication in Qu-Prolog.\textit{Theory and Practice of Logic Programming} . 1 (3), p283-301 
	
	\bibitem{davidW} Keith Clark,Peter J. Robinson,Richard Hagen.(2004) \textit{Beginning .NET game programming in C\#.} United States of America: Apress. 

	\bibitem{xieX} Xiaoyun Xie.(2004) \textit{Distributed Objects System in C\#.} Rochester, United States of America. 

	\bibitem{davidB} David B. Makofske, Michael J. Donahoo, Kenneth L. Calvert.(2004) \textit{TCP/IP sockets in C\#  practical guide for programmers}. Amsterdam: Elsevier.

	\bibitem{normanM} Norman Matloff. (2009) \textit{Tutorial on Network Programming with Python}. California

	\bibitem{guidoR} Guido van Rossum. (1994) \textit{Extending and Embedding the Python Interpreter}. The Netherlands

	\bibitem{sannerM} M. F. SANNER. (1999) \textit{PYTHON: A PROGRAMMING LANGUAGE FOR SOFTWARE
INTEGRATION AND DEVELOPMENT}. California

	\bibitem{kennethC} Kenneth L. Calvert, Michael J. Donahoo. (2008) \textit{TCP/IP Sockets in Java
Practical Guide for Programmers}. Kentucky:Elsevier

	\bibitem{elliotH} Elliot R. Harold, Michael J. Donahoo. (1997) \textit{Java Network Programming}. USA:O'Reilly, p35

	\bibitem{ucam_test_software} 4D Systems. Web. 13th Dec. 2011. \url{http://www.4dsystems.com.au/prod.php?id=82}.

	\bibitem{robertH}Robert Harkness and Malcolm Crook and David Povey.(2007) \textit{Programming Review of Visual Basic.NET for the Laboratory Automation Industry}. Journal of the Association for Laboratory Automation vol.12, p.25-32.
	\url{http://www.sciencedirect.com/science/article/pii/S1535553506005302}.

	\bibitem{gpl} GNU \emph{The GNU Public License version 3} Web. 14th Dec. 2011 \url{http://www.gnu.org/licenses/gpl-3.0.html}

	\bibitem{ccbysa} Creative Commons \emph{Attribution-ShareAlike 2.0 UK: England \& Wales (CC BY-SA 2.0)} Web. 14th Dec. 2011. \url{http://creativecommons.org/licenses/by-sa/2.0/uk/}
	
	\bibitem{fdl} GNU \emph{The GNU Free Documentation License version 1.3} Web. 14th Dec. 2011. \url{http://www.gnu.org/copyleft/fdl.html}

	\bibitem{Huffman} D.A. Huffman \textit{A Method for the Construction of Minimum-Redundancy Codes}. Proceedings of the I.R.E. Sept. 1952. p1098-p1102


	\bibitem{avr_param} Atmel.\textit{megaAVR Parameters} 15th Dec. 2011. \url{http://www.atmel.com/dyn/products/param_table.asp?category_id=163&family_id=607&subfamily_id=760}

	\bibitem{flash_datasheet} \emph{A25L040-U - 16Mbit Low Voltage, Serial Flash Memory With 100MHz Uniform 4KB Sectors - AMIC Technology} 8 Jul. 2010. \url{http://pdf1.alldatasheet.com/datasheet-pdf/view/244476/AMICC/A25L040-U.html}.


\end{thebibliography} 
