% This is part of the FinalReport document.
% Copyright (C) 2011 Piyabhum Sornpaisarn, Andrew Busse, Michael Hodgson, John Charlesworth, Paramithi Svastisinha
% See the file COPYING in FinalReport/ for copying conditions.

\section{Evaluation on Project Efficiency (ps)}
The overall design of our project has been done very effectively.
It fully satisfy the high and medium priorities that we has set it.
The project has been done successfully and the outcomes was very pleased by the customer.
However, the project has been changing throughout the time, especially in the hardware part.
The changes on the structure of the payload communication has changed from the planned one.
The SD card has been added to the payload in order to save the picture on board.
It has been described in detail in section \ref{chap:implementation}
The drawback of this is that we have to assign a task leader for this and so the other task might go slower.
In a group, we have already decided that implementing the SD card will be the best use of our time and human resources.
The microprocessor has changed as well as we describe on section\ref{sec:payload controller}.
Therefore, these changes make the whole project much better and more effective.
Every changes in the design means there will be more time spending to recover the task that have been completed. 
Therefore, we could have done the project better if the task was planned at first so there will be no changes in the middle of the project.
Progressive image downloading was the task that was about to implement and we have put many people to look at it. 
It has been proven that it is possible to implement by the MATLAB simulation (section \ref{sec:progressiveimagedisplay}) and also from a lot of research which the team member has been researching(section\ref{jpeg_image_compression}.
Although it seems like a very promising architecture of send the image, the time limitation make this progressive image impossible to implement on the real device.
In the middle of the project, the group meeting has conclude that the progressive image is taking too much of our human resource time and energy.
Therefore, the task has been omitted and there are big reallocation of people to do other tasks.
This might be a big mistake of the group because we have spent a lot of time doing this task.

