\section{Evaluation on Project Management(ps)}

The specification for this project is challenging and time limiting.
Therefore, the task need to be prioritized so the higher level of importance implement before the other task.
The task with higher risk, has other task depend on it, and long length were the first set of tasks that will do first.
Because we prioritized the tasks so well, we actually have time to implement the entire customer's specification.
However, the low priority tasks that is important to our project has been done but there are some task such as display progress image that have been omitted because of the time limitation.

The project management could be improve in every meeting, each members of the group have to produce a formal documentation in order to keep track and assign the new task.
There are some meeting that we didn't make it as effective as possible.
If the group agreed to implement something on every meeting, it will make the implementation of the project much faster. 

The money we spent on this project that we already described in section\ref{team_resources} is within the budget.
However, we spent a lot on purchasing 3 indentical camera because 2 cameras are faulties and also there are some hardware that we purchased and did not use them.
We could have spend the budget less if we were more careful with the cameras, have a precaution when using the camera and more plan on the purchasing step.

One thing to learn from this project is the delivery of the parts of the project can be very fast or very slow. 
Therefore, before ordering parts, the group should check the delivery time and make sure that the delay has minimum affect on the progress of work.
The hardware arrived on a slightly delay time, therefore some member of the team who assigned to this task has to reallocate to do another task while waiting for them to be delivered.













