\section{Evaluation on Specification}

The specification for this project is challenging and time limiting.
Therefore, the task need to be set up so the higher level of the task is complete first.
The High prioritised criteria has been completed. 
Because we complete capture the image and send it back to the ground station on time for our own deadline, the other medium and low specification have time to be completed.
The time taken of downloading the image that we initially think it will take is about 3 minutes.
By transmitting JPEG image of resolution 640$\times$480 instead of RAW image, the picture takes less than a minute to send it back to the ground station.
Resolution can be chosen by the user on the image viewer program which make the sending of image even faster.
It requires us to cancel the image from downloading, and this has done and it is functional.

We have done well on finishing tasks on time and completing the specification that required by the customer.
The task has been on a good track throughout the project, even though there are some problems on acquiring hardware and some camera faulty which make the delay of tasks.
The other problem that we have is that the payload and the UAV communication occasionally work at first and then we found out that there are some bugs on the UAV.
For this problem, the customers has fix the bug on the UAV and then we can continue working on with the payload.
The camera has been order many times.
This is because the camera is very sensitive to human contact.
However, all the risk has been mentioned and we have precaution if those risk happens.

Because all of the members put their time and power on the project, it went well even though there are many unpredictable problems happens. The risk management has done carefully, so there is no paniking when there are problems happens. Overall, the high and medium priority specification has completed. The low priority that is important to our project has been done but there are some task such as display progress image.





