% --------------------
\chapter{Planning}
% --------------------

\section{Introduction(ps)}
This part will describe the task that has been spliting into milestones which each task has to be complete step by step in order th achieve the final outcome.
The risk mangement has been planned carefully so any risk that is possible has a back up plan for it.
This section also includes work allocation of each member.
It also describes the group resources such as buget, laboratory equipment and customer's supply. 
\section{Initial Milestones - (mh)}
\label{sec:initial_milestones}
A set of milestones have been devised to help track progress and inform test plans.
Each of the milestones represents a real and measurable progress step towards the 
end goals of this project, the milestones were derived from the tasks listed in the initial
Gantt chart (see appendix |||||||||||). It should be noted that these were the initial
milestones derived for the project and were substantially amended throughout the course of
the project in order to keep them relevant - the final state of the amended milestones
can be seen later in section \ref{sec:amended_milestones}.

To assist comprehension the milestones have been arranged into a number of categories,
relating to the way in which the project work has been broken up.

\subsection{Payload Module - Camera Module Communication Milestones}
%\begin{itemize}
	\subsubsection{Milestone: Prototype Camera Module Communication}
	\label{sec:ms_init_prototype_camera_module_comms}
		\begin{itemize}
			\item 	Initial basic communication with a camera module, an image should be
				downloaded from the camera and viewed in some way.
		\end{itemize}

	\subsubsection{Milestone: Payload controller to/from camera module communication}
	\label{sec:ms_init_payload_controller_camera_module}
		\begin{itemize}
			\item 	An image should be downloaded from the camera on to the 
				payload controller hardware.
			\item 	Sub milestones are as follows:
			\begin{itemize}
				\item The payload controller should be capable of changing the
					image resolution of the camera.
				\item The payload controller should be capable of changing the
					colour type of the camera.
			\end{itemize}
		\end{itemize}

%\end{itemize}

\subsection{Payload Module - Image Encoding and Transmission Milestones}
%\begin{itemize}
	\subsubsection{Milestone: Basic Raw Encoding}
		\label{sec:ms_init_basic_raw_encoding}
		\begin{itemize}
			\item 	The payload module should send raw image data in the same form as 
				obtained from the camera via the autopilot link
				to the ground station where it should be saved or viewed in some manner
				to verify the milestone.
		\end{itemize}

	\subsubsection{Milestone: Custom (Progressive/Compressed) Encoding - Matlab Algorithm Prototype}
		\label{sec:ms_init_custom_enc_matlab}
		\begin{itemize}
			\item 	A prototype of progressive encoding prototyped in matlab
				should be implemented. This algorithm should demonstrate how the image
				could be sent progressively and ideally in a compressed form.
		\end{itemize}

	\subsubsection{Milestone: Custom Encoding Algorithm Implementation on Payload Controller}
		\label{sec:ms_init_custom_enc_payload}
		\begin{itemize}
			\item 	Milestone \ref{sec:ms_init_custom_enc_matlab} should be implemented on
				the payload controller module.
		\end{itemize}

	\subsubsection{Milestone: Custom Encoding Data Breakdown and Transmission to Ground Station via Autopilot Link}
		\label{sec:ms_init_custom_breakdown_transmission}
		\begin{itemize}
			\item 	The progressive data produced by milestone
				\ref{sec:ms_init_custom_enc_payload} should be broken down and sent
				via the autopilot link to the ground station.
		\end{itemize}

\subsection{Payload Module Construction Milestones}
Many of the milestones listed above rely upon a working physical implementation of the system at each stage
so these will not be duplicated. However, there are a few milestones which are specific to the physical implementation
of the system.
%Customer Provided `Dummy' Payload Schematics Working

%Camera connection

%Payload communication

	\subsubsection{Milestone: Payload Breadboard Prototype}
		\begin{itemize}
			\item A finalized PCB design ready to be sent for manufacture.
		\end{itemize}

	\subsubsection{Milestone: Payload PCB Design}
		\begin{itemize}
			\item A finalized PCB design ready to be sent for manufacture. 
		\end{itemize}
		
	\subsubsection{Milestone: Complete System on PCB}
		\begin{itemize}
			\item A working system implementation on PCB.
		\end{itemize}

%Final implementation

\subsection{Ground Station Image Viewer Milestones}
	\subsubsection{Milestone: Basic Dummy Server Communications}
		\label{sec:ms_init_basic_dummy_server_comms}
		\begin{itemize}
			\item 	Some prototype programs should be produced to help understand TCP/IP communications.
				One server program serving some test data over a TCP/IP port and one
				client program connecting to this port and sending/receiving test data.
		\end{itemize}

	\subsubsection{Milestone: Communications with Customers Ground Station Sofware}
		\label{sec:ms_init_basestation_comms}
		\begin{itemize}
			\item 	Milestone \ref{sec:ms_init_basic_dummy_server_comms} should be
				completed.
			\item 	Communication with the customers ground station software via TCP/IP console and
				data port. Data should be streamed from some known source and verified correct and
				commands should be sent via the port and verified that they execute in the program.
		\end{itemize}

	\subsubsection{Milestone: Decode Basic Raw Image}
		\label{sec:ms_init_decode_basic_raw_image}
		\begin{itemize}
			\item 	Milestone \ref{sec:ms_init_basestation_comms} should be completed.
			\item 	Data sent from the implementation of \ref{sec:ms_init_basic_raw_encoding} should be
				decoded and saved/displayed on the ground station in some way.
		\end{itemize}

	\subsubsection{Milestone: Custom Decoding - Matlab Implementation}
		\begin{itemize}
			\item 	Milestone \ref{sec:ms_init_custom_enc_matlab} should be completed.
			\item 	Data sent from the implementation of \ref{sec:ms_init_custom_enc_matlab} should be
				decoded and saved/displayed on the ground station in some way. NB: This does not require
				a working payload implementation.
		\end{itemize}

	\subsubsection{Milestone: Custom Decoding - Deployable Implementation}
		\begin{itemize}
			\item 	Milestone \ref{sec:ms_init_decode_basic_raw_image} should be completed.
			\item 	Data sent from the implementation of \ref{sec:ms_init_custom_breakdown_transmission} should be
				decoded and saved/displayed on the ground station in some way.
		\end{itemize}

	\subsubsection{Milestone: Functional User Interface}
		\begin{itemize}
			\item 	A functional user interface that allows users to take images and view them using the implementations
				for the milestones described above.
		\end{itemize}

%\end{itemize}

\input{management_risk}

\input{management_work_allocation}

\input{management_resources}

\section{Group Communication (ab) (ms)}
\label{group_comms}

\subsection{Formal Meetings}
\label{formal meetings}
For the duration of the project, we held weekly meetings on most Tuesday 
Afternoons from 4pm onwards in the Hartley Library. This would allow us to 
review progress made against progress expected, and to modify our project 
plan and allocation of work for the following week.

Minutes of these meetings would be stored in our repository.
The timing of these meetings (the afternoon before our weekly meetings with our 
supervisor) will allow us to present a clear outline 
of new developments and our week-by-week plans to our supervisor.
The meetings with our supervisor will allow the group members to assess their situation
and re-organize themselves if necessary.

\subsection{Methods of Communication (ms)}

The group was prepared to use two primary methods of communication during the project
in-between group meetings. This would allow the group to share any urgent information
with each other easily.
These methods of communication are discussed below:

\subsubsection{E-mail}

Email would be the primary form of communication between group members
in between the weekly group meetings. It will be the responsibility of each group
member to regularly check their e-mail and keep up to date with the latest 
developments of the project. Information which is useful for all members of the 
project or not directed at a specific individual would be sent by e-mail. E-mail also 
has the advantage of communicating software directly between members and leaving
an audit trail to keep track of the project's progress.

\subsubsection{Telephone}

Each group member's contact phone numbers were shared at the beginning of the
project to complement e-mail communications. A contact by phone number would
be useful if very urgent information needs to be communicated immediately between
project members. Although e-mail communication should suffice, telephone 
communication would be used to instantly contact a group member who may not
be keeping up with e-mail exchanges.

\subsection{Source Control}
\label{source control}
We decided to use version control software throughout the project, to manage 
everything from minutes to source code and payload schematics. As well as 
being a very useful tool to facilitate group work, it also helps us to meet 
our customer's request to deliver this as an open source project - at the end 
of the project, a repository could easily be gardened and presented, with the 
addition of appropriate open-source licenses at the end of the project.

Initially, we used a central Subversion (SVN) repository hosted on ECS' 
UGForge service. It was decided to use this as most of the group had 
experience using SVN. This worked well for most of the project, but 
unfortunately, something was committed to this repository that could not be 
open sourced (the customer's Ground Control Station software). This presented 
us with a problem, as although it would be trivial to revert this commit with 
the "\$ svn merge" command, this creates a new commit, and the file in 
question would remain in the repository's history and could still be accessed.

In theory, it would be possible to remove this commit from SVN history by 
using the "\$ svnadmin dump" command, filtering the offending commit out of 
the dumpfile, and regenerate the repository with the "\$ svnadmin load" 
command. However, in practice, this was not possible as our repository 
contains binary information above 64kB, therefore the ASCII editor used to 
modify the dumpfile would cut off data in the binary file after the 64kB 
limit, rendering any following data useless.

It would be possible to start a new SVN repository and check in our 
repository up to but not including the offending commit, but we would lose 
all metadata (i.e. committer, commit time, etc.). Therefore, it was decided to 
switch to git, a distributed version control system (which would allow us to 
modify project history). Converting the repository using git-svn was a trivial 
process. Although not all of the group was confident using this tool, git 
lets a committer commit on behalf of another user. Moving to git also 
allowed us to use github, a hosting service, which is free to open-source 
projects (such as ours), which also provides us with some additional 
project statistics. ??? Reference ???? Appendix ???
